Nested sampling with two objective functions

### 2016-01-07 Paper/ms.tex
Numbers in the algorithm, and failure modes

\begin{algorithm}[ht!]
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
$N$ should quite large (typically 1000 or greater), and the algorithm is
slightly more elegant if $N$ is odd.
\State Initialise the {\em remaining prior mass} to be $M=1$.
\State Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
$\emptyset$.
\While{more iterations desired}
	\State Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
			and sort the $\hat{X}$ values observed.
	\State Find the median $\hat{X}$ value, $\hat{X}_{(k)}$.
	\State Classify all particles as either ``interior'', ``boundary'', or
			``exterior'', based on whether their $\hat{X}$ values are
			greater than, equal to, or less than $\hat{X}_{(k)}$ respectively.
	\State If the number of interior particles $n_{\rm interior}$ or the number
			of exterior particles $n_{\rm exterior}$ is zero, replace $k$ by
			$(k-1)$ (to try a percentile other than the median)
			and go back to the previous step (if $k=1$ then set $k=N$ instead of zero).
	\State Save all ``interior'' particles to disk, assigning each a prior weight of $n_{\rm interior}/(n_{\rm interior} + n_{\rm exterior})$.
	\State Exclude the region in the $L_1$-$L_2$ plane where
$\hat{X} \geq \hat{X}_{(k)}$. That is, set
	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
	\State Update the remaining prior mass to $M \leftarrow M n_{\rm exterior}/N$.
	\State Replace all interior and boundary particles by new
			particles generated from $\pi(\xx)$, subject to the constraint
			of not being in the excluded region.
\EndWhile
\end{algorithmic}
\caption{\label{alg:algorithm}}
\end{algorithm}

@@

@@

>>>>

\begin{algorithm}[ht!]
\begin{algorithmic}
\State 1) Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
$N$ should quite large (typically 1000 or greater), and the algorithm is
slightly more elegant if $N$ is odd.
\State 2) Initialise the {\em remaining prior mass} to be $M=1$.
\State 3) Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
$\emptyset$.
\While{more iterations desired}
	\State i) Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
			and sort the $\hat{X}$ values observed.
	\State ii) Find the median $\hat{X}$ value, $\hat{X}_{(k)}$.
	\State iii) Classify all particles as either ``interior'', ``boundary'', or
			``exterior'', based on whether their $\hat{X}$ values are
			greater than, equal to, or less than $\hat{X}_{(k)}$ respectively.
	\State iv) If the number of interior particles $n_{\rm interior}$ or the number
			of exterior particles $n_{\rm exterior}$ is zero, replace $k$ by
			$(k-1)$ (to try a percentile other than the median)
			and go to step iii) (if $k=1$ then set $k=N$ instead of zero).
	\State v) Save all ``interior'' particles to disk, assigning each a prior weight of $n_{\rm interior}/(n_{\rm interior} + n_{\rm exterior})$.
	\State vi) Exclude the region in the $L_1$-$L_2$ plane where
$\hat{X} \geq \hat{X}_{(k)}$. That is, set
	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
	\State vii) Update the remaining prior mass to $M \leftarrow M n_{\rm exterior}/N$.
	\State viii) Replace all interior and boundary particles by new
			particles generated from $\pi(\xx)$, subject to the constraint
			of not being in the excluded region.
\EndWhile
\end{algorithmic}
\caption{\label{alg:algorithm}}
\end{algorithm}

@@

\section{Failure modes}

If $L_1(\xx)$ and $L_2(\xx)$ are inversely and strongly dependent...

@@

BJB initiated the project and explored various ideas which did not work.
